---
title: "Simulation Report"
author: "Haptic Finance"
date: "June 18, 2022"
output: 
  pdf_document:
      toc: true
      number_sections: true
      keep_md: true
  html_document: default
tables: yes
latex_engine: pdflatex
header-includes:
    - \usepackage{float}
    - \usepackage{pdfpages}
    - \usepackage{tabu}
    - \usepackage{booktabs}
    - \usepackage[justification=raggedright,labelfont=bf,singlelinecheck=false]{caption}
    - \usepackage{array}
    - \usepackage{xcolor} 
    - \usepackage{color, colortbl}

knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "pdf") })
---

\captionsetup[table]{labelformat=empty}
\captionsetup[table]{labelfont=bf}


``` {r results="asis", warning=FALSE, echo=FALSE}

source("init.r")
suppressPackageStartupMessages(library(pdftools))

nDataPoints = nrow(historical_prices_ETH)

historicalPricesETHV <- as.vector(historical_prices_ETH[,3])
historicalPricesHAPV <- as.vector(historical_prices_HAP[,3])

minPriceETH = historicalPricesETHV[which.min(historicalPricesETHV)]
maxPriceETH = historicalPricesETHV[which.max(historicalPricesETHV)]
avgPriceETH = mean(historicalPricesETHV)

minPriceHAP = historicalPricesHAPV[which.min(historicalPricesHAPV)]
maxPriceHAP = historicalPricesHAPV[which.max(historicalPricesHAPV)]
avgPriceHAP = mean(historicalPricesHAPV)

compWeek = comp_weeks[which.max(comp_weeks)]

if (print_full_tables == 1) {
  longTableB <- ifelse(n_borrowers > 30 , TRUE, FALSE)
  longTableS <- ifelse(n_stakers > 30, TRUE, FALSE)
  borrowers_show <- 1:n_borrowers
  stakers_show <- 1:n_stakers
  msg = "*Full report - Long tables active*"
} else {
  longTableB = F
  longTableS = F
  borrowers_show <- 1:10
  stakers_show <- borrowers_show
  msg = glue::glue("*Shortened report - Top ten records sorted by balance shown*.")
}

```

# Historical data

## Summary

Simulation ran over **`r nDataPoints`** weeks. Start date **`r format(as.Date(simulation_start_date), "%d/%b/%Y")`**.

## Price data

```{r echo=FALSE, warning=FALSE, results='asis'}

  options(knitr.duplicate.label = "allow")
  options(scipen=999) # avoid scientific notation
  par(mfrow=c(2,2)) # plots 4 charts per page

  a <- c("ETH/USD", prettyNum(minPriceETH), prettyNum(maxPriceETH), prettyNum(avgPriceETH))
  b <- c("HAP/USD", prettyNum(minPriceHAP), prettyNum(maxPriceHAP), prettyNum(avgPriceHAP))
  pricesMat <- rbind(a,b)

  dfPrices <- data.frame(pricesMat)
  colnames(dfPrices) <- c("Ticker", "Min", "Max", "Avg.")
  dfPrices <-  setNames(dfPrices, c("Ticker", "Min", "Max", "Avg."))
  row.names(dfPrices) <- NULL

  dfPrices %>%
    kbl( caption = "", booktabs = T) %>%
      kable_styling(latex_options = "HOLD_position", position="left") %>%
        kable_classic(full_width = F, html_font = "Cambria") %>%
            print()

```

## Charts

```{r echo=FALSE, warning=FALSE}

options(knitr.duplicate.label = "allow")
options(scipen=999) # avoid scientific notation
par(mfrow=c(2,2)) # plots 4 charts per page

ts_H_ETH = ts(data = historical_prices_ETH[, 3], start = 1, end = nrow(historical_prices_ETH), frequency = 1,  deltat = 1)
matplot(ts_H_ETH, type = "l", main = "ETH/USD", xlab = "Weeks", ylab = "$")

ts_HAP = ts(data = historical_prices_HAP[, 3], start = 1, end = nrow(historical_prices_HAP), frequency = 1,  deltat = 1)
matplot(ts_HAP, type = "l", main = "HAP/USD", xlab = "Weeks", ylab = "$")

borrowers_init = get("borrowers_week_0")
borrowers_final_ = get(glue::glue("borrowers_week_{nrow(historical_prices_ETH)}"))

```
 

# Borrowers (Liquidity on margin)

## Summary

- Initial borrowers **`r n_borrowers`**
- Final borrowers **`r nrow(borrowers_cp)`**
- Initial liquidity **`r prettyNum(sum(borrowers_init[,2]), scientific=FALSE,big.mark=",")`** USD
- Final liquidity **`r prettyNum(sum(borrowers_final_[,2]), scientific=FALSE,big.mark=",")`** USD

## Color legend

```{r echo=F, results='asis'} 

a <- c("brown", "I/L compensation")
b <- c("red", "Liquidation")

colorLegend <- rbind(a,b)

dfClegend <- data.frame(colorLegend)
colnames(dfClegend) <- c("Color", "Operation")
dfClegend <-  setNames(dfClegend, c("Color", "Operation"))
row.names(dfClegend) <- NULL

dfClegend %>%
  mutate(Color = cell_spec(Color, background=ifelse(Color == "brown", "brown", "red"), color=ifelse(Color == "brown", "brown", "red"))) %>% 
    kbl(caption = "", booktabs = T, escape = FALSE) %>%
      kable_styling(latex_options = "HOLD_position", position="left") %>%
        kable_classic(full_width = F, html_font = "Cambria") %>%
          print()

```

## Borrowers by week 

This section is a breakdown of the borrowers data by week. 

`r msg`

```{r, echo=FALSE, warning=FALSE, results='asis'} 

options(knitr.duplicate.label = "allow")
options(scipen=999) # avoid scientific notation
par(mfrow=c(2,2)) # plots 4 charts per page

template <- " %s

"
indexes <- c()
tables <- c()
separators <- c()

for (k in 1:nrow(historical_prices_ETH)) {
  
  prettyETH = prettyNum( historical_prices_ETH[k, 3], big.mark=",", scientific=FALSE)

  indexes <- c(indexes, k)
  borrowers_cp = get(glue::glue("borrowers_week_{k}"))
  borrowers_cp <- borrowers_cp[,-c(5, 6, 8, 9, 10, 12, 13, 14)]

  dfB <- data.frame(borrowers_cp[borrowers_show,])
  colnames(dfB) <- labels_borrowers_2
  dfB <-  setNames(dfB, labels_borrowers_2)
  dfB <- dfB[order(-dfB$sUSD, decreasing = F),] 
  row.names(dfB) <- NULL

  dfB %>% 
   mutate_if(is.numeric, format, digits=2,nsmall = 0) %>% 
    kbl( caption = paste("Week", k, "- ETH/USD", prettyETH,  sep=" "), booktabs = T, escape=F, longtable=longTableB) %>%
     reduce(6:7, function(x, y) {
      col <- dfB[, y]
      column_spec(x, y, background = case_when(
        labels_borrowers_2[y] == "LiqWeek" & col != 0 ~ "red",
        labels_borrowers_2[y] == "Comp-Week" & col != 0 & k == col ~ "brown",
        TRUE ~ "white"), bold = case_when(
        labels_borrowers_2[y] == "LiqWeek" & col != 0 ~ "T",
        labels_borrowers_2[y] == "Comp-Week" & col != 0 ~ "T",
        TRUE ~ "F"))
    }, .init = .) %>%
      kable_styling(latex_options = "HOLD_position") %>%
        kable_classic(full_width = F, html_font = "Cambria") %>%
                column_spec(1:ncol(dfB), width="5.5em") %>%
                  print()

}

```
## Liquidations

```{r, echo=FALSE, warning=FALSE, results='asis'} 

```
- Total borrowers liquidated **`r total_liquidations`**  


## Impermanent loss

Impermanent loss compensations are disbursed denominated in VDebt.

### Compensations

*  All borrowers compensated by week **`r compWeek`**
*  Total compensations **`r comp_counter`**
*  Total disbursed **`r prettyNum(il_compensations_cum, scientific=FALSE,big.mark=",")`** VDebt

## APR 

## Plots
```{r result='asis', echo=FALSE, warning=FALSE}

options(scipen=999) # avoid scientific notation
par(mfrow=c(2,2)) # plots 4 charts per page

ts_ETH = ts(data = randomPricesBorrowersInitial, start = 1, end = n_borrowers, frequency = 1,  deltat = 1)
matplot(ts_ETH, type = "l", main = "ETH/USD", xlab = "VS Borrowers (Open Loan)", ylab = "$")


IL_days = ts(data = impermanent_loss_days, start = 1, end = nrow(historical_prices_ETH), frequency = 1,  deltat = 1)
matplot(IL_days, type = "h", main = "Impermanent loss", xlab = "Weeks", ylab = "$")


if (il_compensations_cum > 0) {
  IL_week = ts(data = il_compensation_period, start = 1, end = length(historical_prices_ETH), frequency = 1,  deltat = 1)
  matplot(il_compensation_period, type = "l", main = "I/L compensation", xlab = "Total compensations", ylab = "VDebt", col=c("blue", "green") )
  IL_days_2 = ts(data = il_compensation_period_w_zeroes, start = 1, end = nrow(historical_prices_ETH), frequency = 1,  deltat = 1)
  matplot(IL_days_2, type = "h", main = "I/L compensation", xlab = "Weeks", ylab = "$")
}

```

```{r results='asis', echo=FALSE, warning=FALSE}

stakingPrices <- as.vector(hap_staking_price[1:nrow(stakers)])

minStakingPrice <- prettyNum(stakingPrices[which.min(stakingPrices)], scientific=F, big.mark=",")
maxStakingPrice <- prettyNum(stakingPrices[which.max(stakingPrices)], scientific=F, big.mark=",")

meanStakingPrice <- stakingPrices %>% mean() %>% prettyNum(scientific=F, big.mark=",")
stakers_init <- get("stakers_week_0")

totalStakedStart <- prettyNum(sum(stakers_init[,1]), scientific=F, big.mark=",")
totalMintedStart <- prettyNum(sum(stakers_init[,2]), scientific=F, big.mark=",")
totalDebtStart  <- prettyNum(sum(stakers_init[,5]), scientific=F, big.mark=",")

totalStakedEnd <- prettyNum(sum(lastStakersSnapshot[,1]), scientific=F, big.mark=",")
totalMintedEnd <- prettyNum(sum(lastStakersSnapshot[,2]), scientific=F, big.mark=",")
totalDebtEnd  <- prettyNum(sum(lastStakersSnapshot[,5]), scientific=F, big.mark=",")

```

# Stakers 

## Summary

- Initial stakers **`r n_stakers`**
- Final stakers **`r nrow(stakers)`**

```{r echo=FALSE, warning=FALSE, results='asis'}

  options(knitr.duplicate.label = "allow")
  options(scipen=999) # avoid scientific notation
  par(mfrow=c(2,2)) # plots 4 charts per page

  a <- c("Start (Week 1)", minStakingPrice, maxStakingPrice,  meanStakingPrice)
  b <- c()
  
  stakingPrices <- rbind(a,b)

  dfStakingPrices <- data.frame(stakingPrices)
  colnames(dfStakingPrices) <- c("Period", "Min.", "Max.", "Avg.")
  dfStakingPrices <-  setNames(dfStakingPrices, c("Period", "Min.", "Max.", "Avg."))

  row.names(dfStakingPrices) <- NULL

  dfStakingPrices %>%
    kbl( caption = paste("Staking prices"), booktabs = T) %>%
      kable_styling(latex_options = "HOLD_position", position="left") %>%
        kable_classic(full_width = F, html_font = "Cambria") %>%
            print()


  a <- c("Start (Week 1)", totalStakedStart, totalMintedStart,  totalDebtStart)
  b <- c(glue::glue("End (Week {nrow(historical_prices_ETH)})"), totalStakedEnd, totalMintedEnd, totalDebtEnd)
  
  stakersMat <- rbind(a,b)

  dfStakersInfo <- data.frame(stakersMat)
  colnames(dfStakersInfo) <- c("Period", "Staked (HAP)", "Minted (VDebt)", "Debt (VDebt)")
  dfStakersInfo <-  setNames(dfStakersInfo, c("Period", "Staked (HAP)", "Minted (VDebt)", "Debt (VDebt)"))
  row.names(dfStakersInfo) <- NULL

  dfStakersInfo %>%
    kbl( caption = "", booktabs = T) %>%
      kable_styling(latex_options = "HOLD_position", position="left") %>%
        kable_classic(full_width = F, html_font = "Cambria") %>%
            print()

```

## Color legend

```{r echo=F, results='asis'} 

a <- c("green", "Fix C-ratio")
b <- c("red", "Liquidation")
c <- c("yellow", "Mint Max")

colorLegend <- rbind(a, b, c)

dfClegend <- data.frame(colorLegend)
colnames(dfClegend) <- c("Color", "Operation")
dfClegend <-  setNames(dfClegend, c("Color", "Operation"))
row.names(dfClegend) <- NULL

dfClegend %>%
  mutate(Color = cell_spec(Color, background=ifelse(Color == "green", "green", ifelse(Color == "yellow", "yellow", "red"))))%>%
    kbl( caption = paste("Color legend"), booktabs = T, escape = FALSE) %>%
      kable_styling(latex_options = "HOLD_position", position="left") %>%
        kable_classic(full_width = F, html_font = "Cambria") %>%
          print()

```

## Debt pool by week

This section is a breakdown of the stakers debt pool by week. 

`r msg`

```{r results='asis', echo=FALSE, warning=FALSE}

for (k in 1:nrow(historical_prices_ETH)) {

  prettyHap = prettyNum( historical_prices_HAP[k, 3], big.mark=",", scientific=FALSE)

  stakers_cp = get(glue::glue("stakers_week_{k}"))
  #print(stakers_cp)
  stakers_cp <- stakers_cp[,-c(3, 4, 5, 6, 8, 10, 11, 13)]
  #print(ncol(stakers_cp))

  stakers_cp <- stakers_cp[,  c(1, 2, 8, 9, 3, 4, 5, 6, 7, 10)]
  stakers <- stakers_cp #params$stakers

  dfStakers <- data.frame(stakers_cp[stakers_show,])
  colnames(dfStakers) <- labels_stakers_short
  dfStakers <- setNames(dfStakers, labels_stakers_short)
  dfStakers <- dfStakers[order(-dfStakers$VDebt, decreasing = F),]
  row.names(dfStakers) <- NULL

  dfStakers %>%
   mutate_if(is.numeric, format, digits=2, nsmall = 0) %>% 
    kbl( caption = paste("Week", k, "- HAP/USD", prettyHap,  sep=" "), booktabs = T, escape=T, longtable=longTableS) %>%
    #row_spec(which(dfStakers$MintMax == 1), bold = T, background = "yellow") %>%
    reduce(8:9, function(x, y) {
      col <- dfStakers[, y]
      column_spec(x, y, background = case_when(
        labels_stakers_short[y] == "LiqWeek" & col != 0  & k == col ~ "red",
        labels_stakers_short[y] == "FixCratio" & col == 1 ~ "green",
        TRUE ~ "white"), bold = case_when(
      labels_stakers_short[y] == "LiqWeek" & col != 0 ~ "T",
      labels_stakers_short[y] == "FixCratio" & col == 1 ~ "T",
      TRUE ~ "F"))
    }, .init = .) %>%
    kable_styling(latex_options = "HOLD_position") %>%
      kable_classic(full_width = F, html_font = "Cambria") %>%
        column_spec(1:ncol(dfStakers), width="4.5em") %>%
          print()
                    
}

total_tda_burned <- prettyNum(total_burned_tda, scientific=F, big.mark=",")

```

## Liquidations

* Total liquidations  **`r total_liquidations`**
* Total stakers liquidated **`r length(unique(stakers_liquidated))`**
* Total burned **`r total_tda_burned`** VDebt

## Hedging

### Options & Perpetuals

## Rewards & APR

The protocol compensate stakers with weekly rewards from the inflationary supply and a percentage of the token swap fees generated by liquidity positions.

### Plots
```{r echo=F, results='asis'}

aprs = c()
avgAprs = c()

for (j in 1:nrow(historical_prices_ETH)) {
  stakers = get(glue::glue("stakers_week_{j}"))
  sumAPR = 0

  for (x in 1:nrow(stakers))   {
    APR = 0
    debtPercentage = stakers[x, 7]
    HAP = stakers[x, 1]
    totalStaked = sum(stakers[, 1])
    totalRewards =  emissions[j, 3] * debtPercentage / 100
    if (stakers[x, 12] >= 390) {
      APR = (totalRewards * historical_prices_HAP[j, 3]) * 52 / totalStaked * historical_prices_HAP[j, 3]
      sumAPR <- sumAPR + (APR * 100)
    } else {
      totalStaked = totalStaked - stakers[x, 1]
      APR = (totalRewards * historical_prices_HAP[j, 3]) * 52 / totalStaked * historical_prices_HAP[j, 3]
    }
  }
  aprs <- c(aprs, sumAPR)

  assign(glue::glue("APR_week_{j}"), aprs)
  avgAprs <- c(avgAprs, mean(aprs))
}

options(scipen = 999) # avoid scientific notation
par(mfrow = c(2,2)) # plots 4 charts per page

ts(data = avgAprs, start = 1, end = nrow(historical_prices_HAP[,]), frequency = 1,  deltat = 1) %>%
matplot( type = "l", main = "Avg. APR", xlab = "Weeks", ylab = "%", col=c("blue"), bg=c("grey"))

total_hap_sold <- prettyNum(total_hap_required, scientific=F, big.mark=",")

```

## Bonds (Stable)

Total sold **`r total_hap_sold`** HAP

```{r echo=F, results='asis'} 

options(scipen = 999) # avoid scientific notation
par(mfrow = c(2,2)) # plots 4 charts per page

#ts(data = hap_required_period, start = 1, end = nrow(historical_prices_ETH), frequency = 1,  deltat = 1) %>%
#matplot(type = "l", main = "HAP sold", xlab = "Weeks", ylab = "HAP", col=c("red"))


```

## Bonds (LP)

## Plots

```{r results='asis', echo=FALSE, warning=FALSE}

options(scipen=999) # avoid scientific notation
par(mfrow=c(2,2)) # plots 4 charts per page

ts(data = hap_staking_price, start = 1, end = n_stakers, frequency = 1,  deltat = 1) %>%
matplot( type = "l", main = "HAP/USD", xlab = "VS Stakers (Mint VDebt)", ylab = "$")

c_ratio_averages <- c()

for (i in 1:nrow(historical_prices_ETH)) {
  mat = get(glue::glue("stakers_week_{i}"))
  averageCratio = mean(mat[,12])
  c_ratio_averages <- c(c_ratio_averages, averageCratio)
}

ts(data = c_ratio_averages, start = 1, end = nrow(historical_prices_ETH), frequency = 1,  deltat = 1) %>%
matplot(type = "l", main = "Network C-ratio", xlab = "Weeks", ylab = "%", col=c("blue"))

debt_by_week <- c()

for (i in 1:nrow(historical_prices_ETH)) {
  mat = get(glue::glue("stakers_week_{i}"))
  total_debt = sum(mat[,2])
  debt_by_week <- c(debt_by_week, total_debt)
}

ts(data = debt_by_week, start = 1, end = nrow(historical_prices_ETH), frequency = 1,  deltat = 1) %>%
matplot(type = "l", main = "Debt", xlab = "Weeks", ylab = "VDebt", col=c("red"))

```

# Emissions

```{r echo=F, result='asis', warning=F}

time <- as.numeric(1:nrow(historical_prices_HAP[,]))  

emissions_weekly_stakers = weekly_emissions[1:length(time)] %>%
  map(function(x) (x * 70) / 100)

emissions_weekly_treasury = weekly_emissions[1:length(time)] %>%
  map(function(x) (x * 30) / 100)

total_emissions <- weekly_emissions[nrow(historical_prices_ETH)] * 1e6
total_emissions_read <- prettyNum(total_emissions, scientific=F, big.mark=",")
total_emissions_stakers <- prettyNum(total_emissions * 0.7, scientific=F, big.mark=",")
total_emissions_treasury <- prettyNum(total_emissions * 0.3, scientific=F, big.mark=",")

```

## Inflationary supply

Total emissions **`r total_emissions_read`** HAP over **`r nrow(historical_prices_ETH)`** weeks.  

## Distribution

```{r echo=F, results='asis'}

a <- c("Stakers", total_emissions_stakers, 70)
b <- c("Treasury", total_emissions_treasury, 30)
  
emission_distribution <- rbind(a,b)

df_emission_distribution <- data.frame(emission_distribution)
colnames(df_emission_distribution) <- c("Actor", "HAP", "%")
df_emission_distribution <-  setNames(df_emission_distribution, c("Actor", "HAP", "%"))
row.names(df_emission_distribution) <- NULL

df_emission_distribution %>%
  kbl( caption = paste(""), booktabs = T) %>%
    kable_styling(latex_options = "HOLD_position", position="left") %>%
      kable_classic(full_width = F, html_font = "Cambria") %>%
          print()

```

## Plots

```{r results='asis', echo = F, warning = F}

options(scipen = 999) # avoid scientific notation
par(mfrow = c(2,2)) # plots 4 charts per page

ts(data = weekly_emissions, start = 1, end = (nrow(historical_prices_HAP[,]) * 8) -1, frequency = 1,  deltat = 1) %>%
matplot( type = "l", main = "Total emissions", xlab = "Weeks", ylab = "HAP (M)", col=c("blue"), bg=c("grey"))

combined <- c(emissions_weekly_stakers, emissions_weekly_treasury)
emissionsMat <- matrix(combined, nrow = length(time))

cols <- hcl.colors(2, palette = "PinkYl")

areaplot(emissionsMat,
         main = "Emissions",
         ylab = "HAP (M)",
         xlab = "Weeks",
         col = cols,
         legend = c("Stakers", "Treasury"),
         args.legend = list(x = "topleft", cex = 0.65,
                            bg = "white", bty = "o"))

total_stable_in_treasury = sum(treasury_balances_period[length(treasury_balances_period)])
total_stable_in_treasury <- prettyNum(total_stable_in_treasury, scientific=F, big.mark=",")
```

# Treasury

## Balances

* **`r prettyNum((30000000 - total_hap_required) + (total_emissions * 0.3), scientific=F, big.mark=",")`** HAP
* **`r total_stable_in_treasury`** sUSD


## Plots

```{r echo=FALSE, results='asis', warning=FALSE}

  options(scipen=999) # avoid scientific notation
  par(mfrow=c(2,2)) # plots 4 charts per page

  ts(data = treasury_balances_period, start = 1, end = nrow(historical_prices_ETH), frequency = 1,  deltat = 1) %>%
  matplot(type = "l", main = "Treasury", xlab = "Weeks", ylab = "$", col=c("green"))

```

# Haptic network token (HAP)

* Total circulating **`r prettyNum(100000000 + total_emissions, scientific=F, big.mark=",")`** HAP.
* Market cap **`r prettyNum((100000000 + total_emissions) * historical_prices_HAP[nrow(historical_prices_HAP), 3], scientific=F, big.mark=",")`** USD

# Tokenized Debt Asset (VDebt)

## Dex performance

VDebt price is `r prettyNum(pool_state[4], scientific=F, big.mark=",")` USD  
Total sold is **`r prettyNum(pool_state[6], scientific=F, big.mark=",")`** VDebt - total sales `r pool_state[5]`  
Total purchased is **`r prettyNum(pool_state[8], scientific=F, big.mark=",")`** VDebt  - total purchases `r pool_state[7]`  


## Charts

```{r echo=F, results='asis'} 

  sD <- sd(historical_data$close)
  

```

Standard deviation is **`r sD`**