---
title: "Simulation Report"
author: "Haptic Finance"
date: "June 17, 2022"
output: 
  pdf_document:
      toc: true
      number_sections: true
      keep_md: true
  html_document: default
tables: yes
latex_engine: pdflatex
header-includes:
    - \usepackage{float}
    - \usepackage{pdfpages}
    - \usepackage{tabu}
    - \usepackage{booktabs}
    - \usepackage[justification=raggedright,labelfont=bf,singlelinecheck=false]{caption}
    - \usepackage{array}
    - \usepackage{xcolor} 
    - \usepackage{color, colortbl}

knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "pdf") })
---

\captionsetup[table]{labelformat=empty}
\captionsetup[table]{labelfont=bf}


``` {r results="asis", warning=FALSE, echo=FALSE}

source("init.r")
suppressPackageStartupMessages(library(pdftools))

nDataPoints = nrow(historicalPricesETH)

historicalPricesETHV <- as.vector(historicalPricesETH[,3])
historicalPricesHAPV <- as.vector(historicalPricesHAP[,3])

minPriceETH = historicalPricesETHV[which.min(historicalPricesETHV)]
maxPriceETH = historicalPricesETHV[which.max(historicalPricesETHV)]
avgPriceETH = mean(historicalPricesETHV)

minPriceHAP = historicalPricesHAPV[which.min(historicalPricesHAPV)]
maxPriceHAP = historicalPricesHAPV[which.max(historicalPricesHAPV)]
avgPriceHAP = mean(historicalPricesHAPV)

compWeek = comp_weeks[which.max(comp_weeks)]

if (print_full_tables == 1) {
  longTableB <- ifelse(n_borrowers > 30 , TRUE, FALSE)
  longTableS <- ifelse(n_stakers > 30, TRUE, FALSE)
  borrowers_show <- 1:n_borrowers
  stakers_show <- 1:n_stakers
  msg = "*Full report - Long tables active*"
} else {
  longTableB = F
  longTableS = F
  borrowers_show <- 1:10
  stakers_show <- borrowers_show
  msg = glue::glue("*Shortened report - Top ten records sorted by balance shown*.")
}

```

# Historical data

## Summary

Simulation ran over **`r nDataPoints`** weeks. Start date **`r format(as.Date(myStartDate), "%d/%b/%Y")`**.

## Price data

```{r echo=FALSE, warning=FALSE, results='asis'}

  options(knitr.duplicate.label = "allow")
  options(scipen=999) # avoid scientific notation
  par(mfrow=c(2,2)) # plots 4 charts per page

  a <- c("ETH/USD", prettyNum(minPriceETH), prettyNum(maxPriceETH), prettyNum(avgPriceETH))
  b <- c("HAP/USD", prettyNum(minPriceHAP), prettyNum(maxPriceHAP), prettyNum(avgPriceHAP))
  pricesMat <- rbind(a,b)

  dfPrices <- data.frame(pricesMat)
  colnames(dfPrices) <- c("Ticker", "Min", "Max", "Avg.")
  dfPrices <-  setNames(dfPrices, c("Ticker", "Min", "Max", "Avg."))
  row.names(dfPrices) <- NULL

  dfPrices %>%
    kbl( caption = "", booktabs = T) %>%
      kable_styling(latex_options = "HOLD_position", position="left") %>%
        kable_classic(full_width = F, html_font = "Cambria") %>%
            print()

```

## Charts

```{r echo=FALSE, warning=FALSE}

options(knitr.duplicate.label = "allow")
options(scipen=999) # avoid scientific notation
par(mfrow=c(2,2)) # plots 4 charts per page

ts_H_ETH = ts(data = historicalPricesETH[, 3], start = 1, end = nrow(historicalPricesETH), frequency = 1,  deltat = 1)
matplot(ts_H_ETH, type = "l", main = "ETH/USD", xlab = "Weeks", ylab = "$")

ts_HAP = ts(data = historicalPricesHAP[, 3], start = 1, end = nrow(historicalPricesHAP), frequency = 1,  deltat = 1)
matplot(ts_HAP, type = "l", main = "HAP/USD", xlab = "Weeks", ylab = "$")

```

```{r echo=F, warning=F, result='asis'} 

  borrowers_init = get("borrowers_week_0")

```

# Borrowers (Liquidity on margin)

## Summary

- Total borrowers **`r n_borrowers`**
- Total liquidity at staking **`r prettyNum(sum(borrowers_init[,2]), scientific=FALSE,big.mark=",")`** USD

## Color legend

```{r echo=F, results='asis'} 

a <- c("brown", "I/L compensation")
b <- c("red", "Liquidation")

colorLegend <- rbind(a,b)

dfClegend <- data.frame(colorLegend)
colnames(dfClegend) <- c("Color", "Operation")
dfClegend <-  setNames(dfClegend, c("Color", "Operation"))
row.names(dfClegend) <- NULL

dfClegend %>%
  mutate(Color = cell_spec(Color, background=ifelse(Color == "brown", "brown", "red"), color=ifelse(Color == "brown", "brown", "red"))) %>% 
    kbl(caption = "", booktabs = T, escape = FALSE) %>%
      kable_styling(latex_options = "HOLD_position", position="left") %>%
        kable_classic(full_width = F, html_font = "Cambria") %>%
          print()

```

## Borrowers by week 

This section is a breakdown of the borrowers data by week. 

`r msg`

```{r, echo=FALSE, warning=FALSE, results='asis'} 

options(knitr.duplicate.label = "allow")
options(scipen=999) # avoid scientific notation
par(mfrow=c(2,2)) # plots 4 charts per page

template <- " %s

"
indexes <- c()
tables <- c()
separators <- c()

for (k in 1:nrow(historicalPricesETH)) {
  
  prettyETH = prettyNum( historicalPricesETH[k, 3], big.mark=",", scientific=FALSE)

  indexes <- c(indexes, k)
  borrowers_cp = get(glue::glue("borrowers_week_{k}"))
  borrowers_cp <- borrowers_cp[,-c(5, 6, 8, 9, 10, 12, 13, 14)]

  dfB <- data.frame(borrowers_cp[borrowers_show,])
  colnames(dfB) <- labels_borrowers_2
  dfB <-  setNames(dfB, labels_borrowers_2)
  dfB <- dfB[order(-dfB$sUSD),] # temp. disable sorting
  
  row.names(dfB) <- NULL

  dfB %>%
    kbl( caption = paste("Week", k, "- ETH/USD", prettyETH,  sep=" "), booktabs = T, escape=F, longtable=longTableB) %>%
     reduce(6:7, function(x, y) {
      col <- dfB[, y]
      column_spec(x, y, background = case_when(
        labels_borrowers_2[y] == "LiqWeek" & col != 0 ~ "red",
        labels_borrowers_2[y] == "Comp-Week" & col != 0 & k == col ~ "brown",
        TRUE ~ "white"), bold = case_when(
        labels_borrowers_2[y] == "LiqWeek" & col != 0 ~ "T",
        labels_borrowers_2[y] == "Comp-Week" & col != 0 ~ "T",
        TRUE ~ "F"))
    }, .init = .) %>%
      kable_styling(latex_options = "HOLD_position") %>%
        kable_classic(full_width = F, html_font = "Cambria") %>%
                column_spec(1:ncol(dfB), width="5.5em") %>%
                  print()

}

```
## Liquidations

```{r, echo=FALSE, warning=FALSE, results='asis'} 

```
- Total borrowers liquidated **`r totalLiquidations`**  


## Impermanent loss

### Compensations

* All borrowers compensated by week **`r compWeek`**
*  Total compensations **`r comp_counter`**
*  Total disbursed **`r prettyNum(il_compensations_cum, scientific=FALSE,big.mark=",")`** TDA

## APR 

## Plots
```{r result='asis', echo=FALSE, warning=FALSE}

options(scipen=999) # avoid scientific notation
par(mfrow=c(2,2)) # plots 4 charts per page

ts_ETH = ts(data = randomPricesBorrowersInitial, start = 1, end = n_borrowers, frequency = 1,  deltat = 1)
matplot(ts_ETH, type = "l", main = "ETH/USD", xlab = "VS Borrowers (Open Loan)", ylab = "$")


IL_days = ts(data = impermanent_loss_days, start = 1, end = nrow(historicalPricesETH), frequency = 1,  deltat = 1)
matplot(IL_days, type = "h", main = "Impermanent loss", xlab = "Weeks", ylab = "$")


if (il_compensations_cum > 0) {
  IL_week = ts(data = il_compensation_period, start = 1, end = length(historicalPricesETH), frequency = 1,  deltat = 1)
  matplot(il_compensation_period, type = "l", main = "I/L compensation", xlab = "Total compensations", ylab = "TDA", col=c("blue", "green") )
  IL_days_2 = ts(data = il_compensation_period_w_zeroes, start = 1, end = nrow(historicalPricesETH), frequency = 1,  deltat = 1)
  matplot(IL_days_2, type = "h", main = "I/L compensation", xlab = "Weeks", ylab = "$")
}

```

```{r results='asis', echo=FALSE, warning=FALSE}

stakingPrices <- as.vector(randomPricesHapStaking[1:nrow(stakers)])

minStakingPrice <- stakingPrices[which.min(stakingPrices)]
maxStakingPrice <- stakingPrices[which.max(stakingPrices)]

meanStakingPrice <- stakingPrices %>% mean()

stakers_init <- get("stakers_week_0")

totalStakedStart <- prettyNum(sum(stakers_init[,1]), scientific=F, big.mark=",")
totalMintedStart <- prettyNum(sum(stakers_init[,2]), scientific=F, big.mark=",")
totalDebtStart  <- prettyNum(sum(stakers_init[,5]), scientific=F, big.mark=",")

totalStakedEnd <- prettyNum(sum(lastStakersSnapshot[,1]), scientific=F, big.mark=",")
totalMintedEnd <- prettyNum(sum(lastStakersSnapshot[,2]), scientific=F, big.mark=",")
totalDebtEnd  <- prettyNum(sum(lastStakersSnapshot[,5]), scientific=F, big.mark=",")

```

# Stakers 

## Summary

- Total stakers **`r n_stakers`**

```{r echo=FALSE, warning=FALSE, results='asis'}

  options(knitr.duplicate.label = "allow")
  options(scipen=999) # avoid scientific notation
  par(mfrow=c(2,2)) # plots 4 charts per page

  a <- c("Start (Week 1)", minStakingPrice, maxStakingPrice,  meanStakingPrice)
  b <- c()
  
  stakingPrices <- rbind(a,b)

  dfStakingPrices <- data.frame(stakingPrices)
  colnames(dfStakingPrices) <- c("Period", "Min.", "Max.", "Avg.")
  dfStakingPrices <-  setNames(dfStakingPrices, c("Period", "Min.", "Max.", "Avg."))

  row.names(dfStakingPrices) <- NULL

  dfStakingPrices %>%
    kbl( caption = paste("Staking prices"), booktabs = T) %>%
      kable_styling(latex_options = "HOLD_position", position="left") %>%
        kable_classic(full_width = F, html_font = "Cambria") %>%
            print()


  a <- c("Start (Week 1)", totalStakedStart, totalMintedStart,  totalDebtStart)
  b <- c(glue::glue("End (Week {nrow(historicalPricesETH)})"), totalStakedEnd, totalMintedEnd, totalDebtEnd)
  
  stakersMat <- rbind(a,b)

  dfStakersInfo <- data.frame(stakersMat)
  colnames(dfStakersInfo) <- c("Period", "Staked (HAP)", "Minted (TDA)", "Debt (TDA)")
  dfStakersInfo <-  setNames(dfStakersInfo, c("Period", "Staked (HAP)", "Minted (TDA)", "Debt (TDA)"))
  row.names(dfStakersInfo) <- NULL

  dfStakersInfo %>%
    kbl( caption = "", booktabs = T) %>%
      kable_styling(latex_options = "HOLD_position", position="left") %>%
        kable_classic(full_width = F, html_font = "Cambria") %>%
            print()

```

## Color legend

```{r echo=F, results='asis'} 

a <- c("green", "Fix C-ratio")
b <- c("red", "Liquidation")

colorLegend <- rbind(a,b)

dfClegend <- data.frame(colorLegend)
colnames(dfClegend) <- c("Color", "Operation")
dfClegend <-  setNames(dfClegend, c("Color", "Operation"))
row.names(dfClegend) <- NULL

dfClegend %>%
  mutate(Color = cell_spec(Color, background=ifelse(Color == "green", "green", "red"), color=ifelse(Color == "green", "green", "red"))) %>% 
    kbl( caption = paste("Color legend"), booktabs = T, escape = FALSE) %>%
      kable_styling(latex_options = "HOLD_position", position="left") %>%
        kable_classic(full_width = F, html_font = "Cambria") %>%
          print()

```

## Debt pool by week

This section is a breakdown of the stakers debt pool by week. 

`r msg`

```{r results='asis', echo=FALSE, warning=FALSE}

for (k in 1:nrow(historicalPricesETH)) {

    prettyHap = prettyNum( historicalPricesHAP[k, 3], big.mark=",", scientific=FALSE)

    stakers_cp = get(glue::glue("stakers_week_{k}"))
    stakers_cp<- stakers_cp[,-c( 3, 4, 6, 8, 10, 11, 13)]
    stakers <- stakers_cp #params$stakers

    dfStakers <- data.frame(stakers_cp[stakers_show,])
    colnames(dfStakers) <- labels_stakers_short
    dfStakers <-  setNames(dfStakers, labels_stakers_short)
    dfStakers <- dfStakers[order(-dfStakers$TDA),] # temp. disable sorting
    row.names(dfStakers) <- NULL

    dfStakers %>%
      kbl( caption = paste("Week", k, "- HAP/USD", prettyHap,  sep=" "), booktabs = T, escape=T, longtable=longTableS) %>%
      reduce(7:8, function(x, y) {
        col <- dfStakers[, y]
        column_spec(x, y, background = case_when(
          labels_stakers_short[y] == "LiqWeek" & col != 0  & k == col ~ "red",
          labels_stakers_short[y] == "FixCratio" & col == 1 ~ "green",
          TRUE ~ "white"), bold = case_when(
        labels_stakers_short[y] == "LiqWeek" & col != 0 ~ "T",
        labels_stakers_short[y] == "FixCratio" & col == 1 ~ "T",
        TRUE ~ "F"))
      }, .init = .) %>%
        kable_styling(latex_options = "HOLD_position") %>%
          kable_classic(full_width = F, html_font = "Cambria") %>%
                  column_spec(1:ncol(dfStakers), width="4.5em") %>%
                    print()
                    
}

```

## Liquidations

* Total liquidations  **`r total_liquidations`**
* Total stakers liquidated **`r length(unique(stakers_liquidated))`**

## Hedging

### Options & Perpetuals

## Rewards & APR

### Bonds (Stable)
### Bonds (LP)

## Plots

```{r results='asis', echo=FALSE, warning=FALSE}

options(scipen=999) # avoid scientific notation
par(mfrow=c(2,2)) # plots 4 charts per page


ts(data = randomPricesHapStaking, start = 1, end = n_stakers, frequency = 1,  deltat = 1) %>%
matplot( type = "l", main = "HAP/USD", xlab = "VS Stakers (Mint TDA)", ylab = "$")

c_ratio_averages <- c()

for (i in 1:nrow(historicalPricesETH)) {
  mat = get(glue::glue("stakers_week_{i}"))
  averageCratio = mean(mat[,12])
  c_ratio_averages <- c(c_ratio_averages, averageCratio)
}

ts(data = c_ratio_averages, start = 1, end = nrow(historicalPricesETH), frequency = 1,  deltat = 1) %>%
matplot(type = "l", main = "Network C-ratio", xlab = "Weeks", ylab = "%", col=c("blue"))

debt_by_week <- c()

for (i in 1:nrow(historicalPricesETH)) {
  mat = get(glue::glue("stakers_week_{i}"))
  totalDebt = sum(mat[,5])
  debt_by_week <- c(debt_by_week, totalDebt)
}

ts(data = debt_by_week, start = 1, end = nrow(historicalPricesETH), frequency = 1,  deltat = 1) %>%
matplot(type = "l", main = "Debt", xlab = "Weeks", ylab = "TDA", col=c("red"))

```

# Emissions

```{r echo=F, result='asis', warning=F}
time <- as.numeric(1:nrow(historicalPricesHAP[,]))  

emissions_weekly_stakers = weekly_emissions[1:length(time)] %>%
  map(function(x) (x * 70) / 100)

emissions_weekly_treasury = weekly_emissions[1:length(time)] %>%
  map(function(x) (x * 30) / 100)

total_emissions <- weekly_emissions[nrow(historicalPricesETH)] * 1e6
total_emissions_read <- prettyNum(total_emissions, scientific=F, big.mark=",")

total_emissions_stakers <- prettyNum(total_emissions * 0.7, scientific=F, big.mark=",")
total_emissions_treasury <- prettyNum(total_emissions * 0.3, scientific=F, big.mark=",")

```

## Inflationary supply

Total emissions **`r total_emissions_read`** HAP over **`r nrow(historicalPricesETH)`** weeks.  

## Distribution

```{r echo=F, results='asis'}

  a <- c("Stakers", total_emissions_stakers, 70)
  b <- c("Treasury", total_emissions_treasury, 30)
  
  emission_distribution <- rbind(a,b)

  df_emission_distribution <- data.frame(emission_distribution)
  colnames(df_emission_distribution) <- c("Actor", "HAP", "%")
  df_emission_distribution <-  setNames(df_emission_distribution, c("Actor", "HAP", "%"))
  row.names(df_emission_distribution) <- NULL

  df_emission_distribution %>%
    kbl( caption = paste(""), booktabs = T) %>%
      kable_styling(latex_options = "HOLD_position", position="left") %>%
        kable_classic(full_width = F, html_font = "Cambria") %>%
            print()

```

## Plots

```{r results='asis', echo = F, warning = F}

options(scipen = 999) # avoid scientific notation
par(mfrow = c(2,2)) # plots 4 charts per page

ts(data = weekly_emissions, start = 1, end = (nrow(historicalPricesHAP[,]) * 8) -1, frequency = 1,  deltat = 1) %>%
matplot( type = "l", main = "Total emissions", xlab = "Weeks", ylab = "HAP (M)", col=c("blue"), bg=c("grey"))

combined <- c(emissions_weekly_stakers, emissions_weekly_treasury)
emissionsMat <- matrix(combined, nrow = length(time))

cols <- hcl.colors(2, palette = "PinkYl")

areaplot(emissionsMat,
         main = "Emissions",
         ylab = "HAP (M)",
         xlab = "Weeks",
         col = cols,
         legend = c("Stakers", "Treasury"),
         args.legend = list(x = "topleft", cex = 0.65,
                            bg = "white", bty = "o"))

```

# Treasury
```{r results='asis', echo=FALSE, warning=FALSE}
```
## Balances

## Plots

```{r echo=FALSE, results='asis', warning=FALSE}

  options(scipen=999) # avoid scientific notation
  par(mfrow=c(2,2)) # plots 4 charts per page

  treasury_balance = ts(data = treasury_balances_period, start = 1, end = nrow(historicalPricesETH), frequency = 1,  deltat = 1)
  matplot(treasury_balance, type = "l", main = "Treasury", xlab = "Weeks", ylab = "$", col=c("green"))


```

# Tokenized Debt Asset (TDA)

## Dex performance

## Charts